Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-13 paper/paper.tex
add list of all stimuli in appendix

We consider a list of 15 instruments: violin (Vn), viola (Va), cello (Vc), contrabass (Cb), concert harp (Hp), Spanish guitar (Gtr), flute (Fl), soprano clarinet (BbCl), alto saxophone (ASax), oboe (Ob), bassoon (Bn), trumpet in C (TpC), French horn (Hn), tenor trombone (TTbn), and bass tuba (BBTb). % TODO check tuba abbreviation
Among this list, the former six are strings, the next five are woodwind, and the last five are brass.
Each of these instruments affords a panel of playing techniques ranging in size between X and Y. % TODO update with numbers
Furthermore, independently of the playing technique, some instruments may be temporarily equipped with timbre-altering mutes, such as a rubber sordina on the bridge of a violin or an aluminium ``wah-wah'' inside in the bell of a trumpet.

@@

>>>>

We consider a list of 16 instruments: violin (Vn), viola (Va), cello (Vc), contrabass (Cb), concert harp (Hp), Spanish guitar (Gtr), accordion (Acc), flute (Fl), soprano clarinet (BbCl), alto saxophone (ASax), oboe (Ob), bassoon (Bn), trumpet in C (TpC), French horn (Hn), tenor trombone (TTbn), and bass tuba (BBTb). 
Among this list, the former six are strings, the next five are woodwind, and the last five are brass.
Some of these instruments may be temporarily equipped with timbre-altering mutes, such as a rubber sordina on the bridge of a violin or an aluminium ``wah-wah'' inside in the bell of a trumpet.
Once augmented with mutes, the list of 16 instruments grows up to X. % TODO complete
Furthermore, every instrument, whether equipped with a mute or not, affords a panel of playing techniques ranging in size between X (for the X) and Y (for the Y). % TODO update with number.
In total, the feasible triplets of instrument, mute, and technique amount to a list of $N=235$ combinations.

% TODO explain the conundrum leading to reduce the dataset size.

@@

\begin{table}
\caption{Full list of audio stimuli (1/2).}
      \begin{tabular}{llll}
          name & instrument  & mute   &  playing technique \\ \hline \hline
        \texttt{ASax-key-cl-C4-p} & Alto saxophone & & key click \\
        \texttt{ASax-ord-C4-mf} & Alto saxophone &  &  \\
        \texttt{ASax-ord-hi-reg-C6-mf} & Alto saxophone &   & \\ 
        \texttt{ASax-slap-C4-mf} & Alto saxophone & & slap tonguing \\ 
        \texttt{ASax-slap-unp-C4-p} & Alto saxophone & & unpitched slap tonguing \\ \hline
        \texttt{BbCl-key-cl-C4-pp} & Soprano clarinet & & key click \\
        \texttt{BbCl-ord-hi-reg-A6-ff} & Soprano clarinet & & \\ \hline
        \texttt{BBTb-explo-slap-C\#1-mf} & Bass tuba &  & explosive slap \\ 
		\texttt{BBTb-pdl-tone-F1-mf} & Bass tuba & & pedal tone \\
		\texttt{BBTb-slap-F1-mf} & Bass tuba & & slap tonguing \\
		\texttt{BBTb-slap-unp-mf-1} & Bass tuba & & unpitched slap tonguing \\ \hline
		\texttt{Bn-key-cl-C3-mf} & Bassoon & & key click \\
		\texttt{Bn-ord-C4-mf} & Bassoon & & \\ \hline
		\texttt{Cb-pizz-bartok-C4-ff-1c} & Contrabass & & pizzicato Bart\'ok (snap) \\
		\texttt{Cb-pizz-lv-C4-mf-1c} & Contrabass & & pizzicato \& \emph{laissez vibrer} \\
        \texttt{Cb-pizz-sec-C4-mf-1c} & Contrabass & & pizzicato secco \\
        \texttt{Cb-pont-C4-mf-1c} & Contrabass & & sul ponticello \\ \hline
        \texttt{Fl-key-cl-C4-f} & Flute & & key click \\
        \texttt{Fl-ord-C4-mf} & Flute & & \\
        \texttt{Fl-tng-ram-C4-mf} & Flute & & tongue ram \\ \hline
        \texttt{Gtr-ord-C4-mf-2c} & Spanish guitar & & \\
        \texttt{Gtr-ord-hi-reg-E5-mf-3c} & Spanish guitar & & \\
        \texttt{Gtr-pizz-bartok-C4-ff-2c} & Spanish guitar & & pizzicato Bart\'ok\\
        \texttt{Gtr-pizz-C4-mf-2c} & Spanish guitar &  & pizzicato \\ \hline
        \texttt{Hn-ord-C4-mf} & French horn & & \\
        \texttt{Hn-slap-C4-mf} & French horn & & slap tonguing \\ \hline
        \texttt{Hp-harm-fngr-C4-f} & Harp & & harmonic fingering \\
        \texttt{Hp-ord-C4-m4} & Harp & & \\
        \texttt{Hp-pizz-bartok-C4-mf} & Harp & & pizzicato Bart\'ok \\
        \texttt{Hp-xyl-C4-p} & Harp & & xylophonic \\ \hline
        \texttt{Ob-blow-no-reed-C4} & Oboe & & blow without reed \\
        \texttt{Ob-key-cl-C4-pp} & Oboe & & key click \\
        \texttt{Ob-ord-C4-mf} & Oboe & & \\ \hline
        \texttt{TpC-ord-C4-mf} & Trumpet in C & & \\
        \texttt{TpC-pdl-tone-F3-mf} & Trumpet in C & & pedal tone \\
        \texttt{TpC-slap-C4-p} & Trumpet in C & & slap tonguing \\
        \texttt{TpC+C-ord-C4-mf} & Trumpet in C & cup & \\
        \texttt{TpC+H-ord-C4-mf} & Trumpet in C & harmon & \\
        \texttt{TpC+S-ord-C4-mf} & Trumpet in C & straight & \\
        \texttt{TpC+W-ord-closed-C4-mf} & Trumpet in C & wah (closed) & \\
        \texttt{TpC+W-ord-open-C4-mf} & Trumpet in C & wah (open) & \\ \hline
        \texttt{TTbn-ord-C4-mf} & Tenor trombone & &  \\ 
        \texttt{TTbn+C-ord-C4-mf} & Tenor trombone & cup & \\ 
        \texttt{TTbn+H-ord-C4-mf} & Tenor trombone & harmon & \\
        \texttt{TTbn+S-ord-C4-mf} & Tenor trombone & straight & \\
        \texttt{TTbn+W-ord-closed-C4-mf} & Tenor trombone & wah (closed) & \\
        \texttt{TTbn+W-ord-open-C4-mf} & Tenor trombone & wah (open) & \\ \hline
        \texttt{Va-art-harm-C5-mf-4c} & Viola & & artificial harmonic \\
        \texttt{Va-legno-batt-C4-mf-3c} & Viola & & col legno battuto \\
        \texttt{Va-ord-C4-mf-3c} & Viola & & \\
        \texttt{Va-pizz-bartok-C4-ff-3c} & Viola & & pizzicato Bart\'ok \\
        \texttt{Va-pizz-lv-C4-mf-3c} & Viola & & pizzicato \& \emph{laissez vibrer} \\
        \texttt{Va-pizz-sec-C4-mf-3c} & Viola & & pizzicato secco \\
        \texttt{Va-pont-C4-mf-3c} & Viola & & sul ponticello \\
        \texttt{Va+S-ord-C3-mf-3c} & Viola & sordina & \\
        \texttt{Va+SP-ord-D4-mf-2c} & Viola & piombo & \\ \hline
        \texttt{Vc-art-harm-C4-mf} & Cello & & artificial harmonic \\
        \texttt{Vc-legno-batt-C4-mf-1c} & Cello & & col legno battuto \\
        \texttt{Vc-legno-tratto-C4-mf-1c} & Cello & & col legno tratto \\
        \texttt{Vc-nonvib-C4-mf-1c} & Cello & & nonvibrato \\
        \texttt{Vc-ord-C4-mf-1c} & Cello & & \\
        \texttt{Vc-pizz-bartok-C4-ff-1c} & Cello & & pizzicato Bart\'ok \\
        \texttt{Vc-pizz-lv-C4-mf-1c} & Cello & & pizzicato \& \emph{laissez vibrer} \\
        \texttt{Vc-pizz-sec-C4-mf-1c} & Cello & & pizzicato secco \\
        \texttt{Vc-pont-C4-mf-2c} & Cello & & sul ponticello \\
        \texttt{Vc-tasto-C4-mf-1c} & Cello & & sul tasto \\
        \texttt{Vc+S-ord-C4-mf-1c} & Cello & sordina & \\
        \texttt{Vc+SP-ord-C4-mf-1c} & Cello & piombo & \\ \hline
    \end{tabular}
\end{table}

\begin{table*}
\caption{Full list of audio stimuli (2/2).}
\begin{tabular}{llll}
          name & instrument  & mute   &  playing technique \\ \hline \hline
          \texttt{Vn-art-harm-G5-mf-4c} & Violin & & artificial harmonic \\
          \texttt{Vn-legno-batt-C4-mf-4c} & Violin & & col legno battuto \\
          \texttt{Vn-nonvib-C4-mf-4c} & Violin & & nonvibrato \\
          \texttt{Vn-ord-C4-mf-4c} & Violin & & \\
          \texttt{Vn-pizz-bartok-C4-ff-4c} & Violin & & pizzicato Bart\'ok \\
          \texttt{Vn-pizz-lv-C4-mf-4c} & Violin & pizzicato \& \emph{laissez vibrer} \\
          \texttt{Vn-pizz-sec-C4-mf-4c} & Violin & pizzicato secco \\
          \texttt{Vn-pont-C4-mf-4c} & Violin & & sul ponticello \\
          \texttt{Vn+S-ord-C4-mf-4c} & Violin & sordina & \\
          \texttt{Vn+SP-ord-C4-mf-4c} & Violin & piombo & \\ \hline
\end{tabular}
\end{table*}
